resistanceModelNotesAndy

### 2015-03-11 resistanceModelNotesAndy.Rmd
recording progress

Editing `malaria_code_andy2.r`, indenting functions etc.

@@

**10/3/15** 4.15 -

@@

listFunctions("malaria_code_andy.R")
```

@@

@@

1. created repo on github
1. created RStudio project from github repo

@@

1. create a Github repo and just put my edited file from Beth in to start
1. create a readme.md file
1. ? create an RStudio project for the initial version
1. later, structure as R package, maybe move to a new github repo

>>>>

Editing `malaria_code_andy.r`, indenting functions etc.

@@

**10/3/15** 4.15 - 7.15 3hrs

@@

listFunctions("malaria_code_fromBeth.R")
```

@@

allele.freq : function (mat)  
curtis_f1 : function (nrelaxmat, relaxmat, gencol, r1col)  
curtis_f2 : function (combmat, bmat, amat, gencol, r1col, r2col)  
curtis_ld : function (resultsmat, relaxedmat, gencol, ldcol)  
haplotype : function (mat)  
HW : function (P, mat)  
linkage : function (mat)  
make.genotypemat : function (P_1, P_2)  
make.matrix : function (mat, rnames)  
singlealleleFrequency : function (locus, max_gen, results.list, input)  
timetoFifty : function (locus, max_gen, results.list, input

@@

1. created repo on github
1. created RStudio project from github repo
+ To get ssh push working.
+ RStudio Tools, Shell
+ git remote set-url origin git@github.com:AndySouth/resistance.git

**11/3/15** 9.30

moved my dropbox folder back to C.

@@

1. copy R functions out of `malaria_code_andy` into their own files in an R folder
1. add roxygen documentation for functions
1. later, structure as R package, maybe move to a new github repo
